Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-02-01 docs/msr.tex
added version count graph
added categorisation from maven (table)

\author{
\IEEEauthorblockN{Dimitris Mitropoulos \and Vassilios Karakoidas \and Panos Louridas \and Diomidis Spinellis}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: \{dimitro, bkarak, louridas, dds\}@aueb.gr}
\and
\IEEEauthorblockN{Georgios Gousios}
\IEEEauthorblockA{Department of Software and Computer Technology\\
Delft University of Technology \\
Email: G.Gousios@tudelft.nl}
}

@@

\begin{table}
\centering
\caption{Descriptive Statistics Measurements for the Maven Repository}
\label{tbl:repository}
\begin{tabular}{l r}
 \hline
Projects & 17,505\\
Versions (total) & 114,399\\
Min & 1\\
Max & 337\\
Mean & 6.54\\
Median & 3\\
Range & 336\\
1$^{st}$ Quartile & 1\\
3$^{rd}$ Quartile & 8\\
\hline
\end{tabular}
\end{table}

@@

>>>>

\author{
\IEEEauthorblockN{Dimitris Mitropoulos Vassilios Karakoidas Panos Louridas Diomidis Spinellis}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: \{dimitro, bkarak, louridas, dds\}@aueb.gr}
\and
\IEEEauthorblockN{Georgios Gousios}
\IEEEauthorblockA{Department of Software and Computer Technology\\
Delft University of Technology \\
Email: G.Gousios@tudelft.nl}
}

@@

\begin{figure*}
	\centering
	\includegraphics[scale=0.6]{version_count.pdf}
	\caption{Distribution of version count amongst project population}
	\label{fig:version-count}
\end{figure*}

\begin{table}
\centering
\caption{Descriptive Statistics Measurements for the Maven Repository}
\label{tbl:repository}
\begin{tabular}{l r}
\hline
Measurement & Value\\
 \hline
Projects & 17,505\\
Versions (total) & 114,399\\
Min & 1\\
Max & 337\\
Mean & 6.54\\
Median & 3\\
Range & 336\\
1$^{st}$ Quartile & 1\\
3$^{rd}$ Quartile & 8\\
\hline
\end{tabular}
\end{table}

@@

\subsection{Bug Categorisation and Overview}
\label{sec:bug}

\begin{table}
\centering
\caption{Bug Categorisation according to FindBugs}
\label{tbl:bug-categorisation}
\begin{tabular}{l r}
 \hline
Category & Description\\
\hline
Bad Practice & \\
Correctness & \\
Experimental & \\
Internationalisation & \\
Multi-Threaded Correctness & \\
Performance & \\
Style & \\
Security & \\
\hline
\end{tabular}
\end{table}
